Large language model (LLM) agents are increasingly deployed on data-science tasks, yet existing benchmarks report only aggregate success rates, masking \emph{where} and \emph{why} agents fail. In this work we introduce \textbf{AgentFail}, a diagnostic framework that decomposes every agent failure into five stages---Analytical-Plan, Code-Generation, Runtime, Output-Mismatch, and Answer-Error---and distinguishes \emph{silent failures} (code executes without error but yields a wrong answer) from \emph{loud failures} (code crashes). We further propose \emph{oracle-guided counterfactual repair}, which re-executes a failed trace with the originating step replaced by the ground-truth action to test repairability, and include negative controls (random-step intervention) to measure specificity. We evaluate five frontier LLMs across 4{,}875 runs on three task suites: 80 controlled trap tasks, 23 real UCI datasets, and 200 real DSBench financial-analysis tasks. Our findings reveal a task-dependent failure bifurcation: on synthetic trap tasks the corrected silent-failure rate (SFR) reaches 98\%, while on real UCI data it drops to 4\% and on DSBench to 19\%. A null-model analysis ($R^2=0.605$) shows that 60\% of SFR variation is a mechanical consequence of execution-success-rate differences, but 40\% reflects additional structure. Critically, agents never self-correct: recovery rate is 0\% across all five models and 4{,}875 runs. A failure-aware verifier helps only the lowest-performing model (Qwen3-max, $+24.9\%$, $p<0.001$) but harms stronger models. Oracle-guided repair succeeds on 66\% of failed tasks where ground-truth code is available. The taxonomy achieves moderate inter-rater agreement (Cohen's $\kappa=0.435$) with an LLM-as-judge annotator. We release all code, data, and 4{,}875 annotated traces.
