\section{Annotation Protocol and Results}
\label{app:annotation}

We provide a 47-trace annotation set sampled stratified by model from all 3{,}940 failures. Three independent annotators (blind to system labels) labelled each trace with (stage, subcategory, is\_silent) following the annotation guide. Cohen's $\kappa$ is computed pairwise and Fleiss' $\kappa$ across all annotators. Results: Fleiss' $\kappa = 0.860$ for stage (strong agreement), $0.881$ for is\_silent. Pairwise Cohen's $\kappa$: 0.798, 1.000, 0.798. Full agreement: 89.4\%. The rule-based classifier achieves 71.8\% accuracy against adjudicated gold labels (majority vote), with systematic bias toward \texttt{output\_mismatch} over \texttt{runtime} (precision 1.00, recall 0.52 for output\_mismatch; precision 0.59, recall 1.00 for runtime). The annotation guide, JSON form, individual labels, and gold labels are released with the code.

\section{Harness Ablation Details}
\label{app:harness}

\Cref{tab:harness-ablation} reports the full harness ablation results on synthetic tasks. We also ran the same three harnesses on all 23 UCI tasks (3 repetitions each), with consistent results: GPT-4o shows SFR of 100\% (H1), 31\% (H2), and 100\% (H3) on UCI, matching the synthetic pattern (100\%/30\%/100\%). This confirms silent failures are not an artifact of the minimal ReAct design across both task types.

\input{tables/table_harness_ablation}

\section{Recovery Benchmark Details}
\label{app:recovery}

The recovery benchmark (\Cref{sec:res-recovery-bench}) tests 100 failed traces (80 silent + 20 loud) under 6 feedback conditions, yielding 600 runs. Overall recovery rate is 15.7\%. The key finding is the asymmetry between failure types: loud failures recover at 36.7\% (44/120) while silent failures recover at only 10.4\% (50/480), confirming that silent failures remain substantially harder to correct even with explicit feedback signals.

\section{Reproducibility}
\label{app:repro}

All experiments use deterministic data generation (fixed seeds for synthetic tasks) and temperature-0 LLM calls. The framework includes a deterministic MockLLM that reproduces the full pipeline without API cost. Real-model experiments use the ChatAnywhere OpenAI-compatible endpoint. Total API cost: \$80. Code and data: \url{https://github.com/llmnjust-afk/KDD2027_Work2}.

\section{Data Availability}
\label{app:data-avail}

All code, data, and traces are publicly available at \url{https://github.com/llmnjust-afk/KDD2027_Work2}. The repository includes: (1) the full AgentFail framework source code; (2) the enriched manifest (\texttt{manifest\_v3.csv}) with 32 fields and 5{,}984 runs, of which 3{,}602 are valid runs with automatically generated diagnostic labels; (3) the 47-trace annotation set with full Thought/Code/Output data; (4) the MockLLM backend for zero-cost reproduction; (5) all table-generation scripts with assertion checks; (6) \texttt{requirements.txt} for dependency pinning. The synthetic task generators are self-contained. UCI datasets are downloaded at runtime from public repositories. DSBench tasks require a separate download from~\citep{jing2024dsbench}. Raw LLM responses are not redistributed.

