\section{Data Card and Benchmark Documentation}
\label{app:datacard}

\subsection{Task Suite Descriptions}

\textbf{Synthetic trap tasks (95 tasks).} Programmatically generated across 5 domains (tabular EDA, time-series, recommendation, statistical, text-log) with deterministic ground-truth answers. Each domain uses 16 task instances generated from a fixed seed (seed$=$16). Tasks share structural templates within each domain but use different generated data, producing 70/80 unique answers (87.5\% uniqueness). Near-duplicate questions (identical first 100 chars) exist within domains (55/80) due to shared question structure, but the underlying data and expected answers differ. Train/dev/test splits are by task ID, not by template, so the same template appears in all splits---this is intentional, as the goal is to evaluate failure diagnosis, not template memorisation.

\textbf{UCI real-data tasks (23 tasks).} Analytical questions on 6 public datasets (Iris, Titanic, Tips, MPG, Penguins, Flights) downloaded at runtime from public repositories. Answers are computed deterministically from the real data. Tasks cover groupby aggregation, correlation, counting, and filtering.

\textbf{DSBench real tasks (200 tasks).} Real financial-analysis questions from ModelOff competitions~\citep{jing2024dsbench}, using original multi-sheet Excel workbooks. Answers are multiple-choice (A--I) or numeric. Tasks require understanding complex financial data structures.

\subsection{Contamination and Template Analysis}
\label{app:contamination}

The synthetic tasks are generated from 5 templates (one per domain), each producing 16 instances with different data. The answer distribution shows 70/80 unique answers (87.5\%), with the most common answer appearing in only 4 tasks. This indicates low risk of answer-pattern memorisation. The train/dev/test split (198/42/43 tasks) is stratified by task ID across all suites; since the same template appears in all splits, models cannot exploit template-specific patterns. For DSBench, the tasks originate from public ModelOff competitions and may have appeared in LLM training data; we do not claim contamination-free evaluation for DSBench, only diagnostic trace analysis.

\subsection{Task Difficulty Distribution}
\label{app:difficulty}

We characterise task difficulty by the baseline success rate aggregated across all five models. \Cref{tab:difficulty} reports the distribution. Synthetic tasks span the full difficulty range (19 easy, 63 medium, 13 hard); UCI tasks are uniformly medium-hard; DSBench tasks are almost entirely hard (197 of 200 tasks have SR $<$ 25\%), reflecting the complexity of real financial data.

\begin{table}[t]
\centering
\caption{Task difficulty distribution by suite. Easy: SR $\geq$ 75\%; Medium: 25\% $\leq$ SR $<$ 75\%; Hard: SR $<$ 25\%.}
\label{tab:difficulty}
\small
\begin{tabular}{@{}lcccc@{}}
\toprule
Suite & Tasks & Easy & Medium & Hard \\
\midrule
Synthetic & 95 & 19 & 63 & 13 \\
UCI & 23 & 0 & 21 & 2 \\
DSBench & 200 & 0 & 3 & 197 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Expected Baseline Performance}
\label{app:baselines}

\Cref{tab:baselines} reports the expected baseline performance for each model and suite, providing reference points for future work. DeepSeek-V3 is the strongest on synthetic (88.4\%) and UCI (94.2\%) tasks. DSBench is challenging for all evaluated models (0--3.3\%).\begin{table}[t]
\centering
\caption{Baseline success rates (\%) by model and suite. ``n/a'' indicates API rate limiting prevented evaluation.}
\label{tab:baselines}
\small
\begin{tabular}{@{}lccc@{}}
\toprule
Model & Synthetic & UCI & DSBench \\
\midrule
DeepSeek-V3 & \textbf{88.4} & \textbf{94.2} & 0.0 \\
GPT-4o-mini & 73.9 & 82.6 & 0.8 \\
GPT-4o & 62.1 & 91.3 & \textbf{3.3} \\
Qwen3-max & 18.2 & 0.0 & 3.0 \\
DeepSeek-R1 & 0.0 & 0.0 & n/a \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Data Schema}

Each run in the enriched manifest (\texttt{manifest\_v3.csv}, 30 fields) contains:

\begin{itemize}[leftmargin=*,itemsep=1pt]
\item \texttt{task\_id}, \texttt{suite}: task identifier and suite (\texttt{synthetic}/\texttt{uci}/\texttt{dsbench})
\item \texttt{model}, \texttt{model\_snapshot}, \texttt{provider}: model name, version info (rolling alias vs pinned snapshot), API provider
\item \texttt{harness}, \texttt{variant}: agent harness type and experiment variant (\texttt{baseline}/\texttt{verifier})
\item \texttt{rep}: repetition index (0--2)
\item \texttt{api\_status}, \texttt{parser\_status}, \texttt{execution\_status}: infrastructure status
\item \texttt{task\_correct}: whether the final answer matches ground truth
\item \texttt{observability}: \texttt{success}/\texttt{silent}/\texttt{loud}
\item \texttt{failure\_stage}, \texttt{failure\_subcategory}: five-stage taxonomy label and subcategory
\item \texttt{is\_infra\_failure}, \texttt{infra\_subtype}: infrastructure failure flag and subtype (\texttt{api\_error}/\texttt{unknown}/\texttt{none})
\item \texttt{originating\_step}, \texttt{propagation\_depth}: failure localisation and spread
\item \texttt{is\_silent}, \texttt{recovered}: silent failure flag and recovery status
\item \texttt{tokens}, \texttt{tokens\_input}, \texttt{tokens\_output}, \texttt{cost\_usd}: token usage and cost
\item \texttt{final\_answer}: agent's final answer (truncated to 200 chars)
\item \texttt{label\_source}: \texttt{rule} (rule-based classifier) or \texttt{unmatched}
\item \texttt{annotation\_confidence}, \texttt{human\_gold}, \texttt{adjudication\_status}: human annotation fields (populated for 47 traces; pending for the remainder)
\end{itemize}

\textbf{Annotation uncertainty.} The \texttt{label\_source} field indicates whether a label comes from the rule-based classifier (\texttt{rule}) or is unmatched. For 47 traces, three human annotators provided independent labels and an adjudicated gold label (majority vote); inter-annotator agreement is Fleiss' $\kappa = 0.860$ (strong). The rule-based classifier achieves 71.8\% accuracy against gold labels. The remaining traces retain only rule-based labels; scaling human annotation to 300--500 traces is future work.

\textbf{Missing and duplicate runs.} The manifest contains 5{,}984 runs. Some (task, model, variant) groups have fewer than 3 repetitions due to API failures or timeouts; these are retained with \texttt{api\_status}$=$\texttt{error}. Duplicate runs (same task, model, variant, rep) are detected by the assertion checks and removed. Infrastructure-failed runs are retained in the manifest (for transparency) but excluded from valid-run analyses via the \texttt{is\_infra\_failure} filter.

\subsection{Provenance and Reproducibility}

All experiments use deterministic data generation (fixed seed$=$16 for synthetic tasks) and temperature-0 LLM calls. The framework includes a MockLLM backend that reproduces the full pipeline without API cost. Real-model experiments use the ChatAnywhere OpenAI-compatible endpoint (API calls: June--July 2026). Total API cost: \$80. Note that four of five model identifiers (\texttt{gpt-4o}, \texttt{gpt-4o-mini}, \texttt{deepseek-chat}, \texttt{deepseek-reasoner}) are rolling aliases whose underlying model may change; only \texttt{qwen3-max-2026-01-23} is a pinned snapshot. Repetition agreement under temperature 0 is 89.9\%, with disagreement attributed to server-side non-determinism. The repository includes a \texttt{requirements.txt} for dependency pinning and MD5 checksums for key artifacts (\texttt{manifest\_v3.csv}: \texttt{29ceae8...}, \texttt{manifest.csv}: \texttt{6e2f809...}). A Docker image is planned for the camera-ready version.

\subsection{Answer Evaluation Details}

Answers are evaluated as follows: (1) \emph{Numeric answers}: compared with a relative tolerance of $10^{-3}$ (e.g., \texttt{abs(agent - gt) / max(abs(gt), 1e-9) < 1e-3}). (2) \emph{String answers}: normalised by stripping whitespace, converting to lowercase, and removing punctuation before exact match. (3) \emph{Multiple-choice answers} (DSBench): matched on the letter (A--I) only, ignoring surrounding text. (4) \emph{Tuple answers} (e.g., ``(species, value)''): each component is evaluated independently; both must match. The evaluator code is in \texttt{agentfail/benchmark/tasks.py}.

\subsection{Known Issues}

\begin{itemize}[leftmargin=*,itemsep=1pt]
\item DeepSeek-R1 produces no valid traces on any suite (100\% infrastructure failure); its results should not be interpreted as model inability.
\item DeepSeek-V3 on DSBench: all 600 runs are infrastructure failures (tokens$=$0), likely due to Excel parsing issues in the sandbox.
\item Qwen3-max on UCI: all 69 runs are infrastructure failures.
\item The rule-based classifier achieves 71.8\% accuracy against human gold labels ($\kappa = 0.438$), with systematic bias toward \texttt{output\_mismatch} over \texttt{runtime}; human annotation currently covers 47 of 3{,}940 failures.
\item DSBench tasks require a separate download and may be present in LLM training data.
\end{itemize}

\subsection{Licensing and Maintenance}

The code is released under an open-source license (MIT). The synthetic task generators are self-contained and require no external data. UCI datasets are public domain. DSBench tasks are used under their original license~\citep{jing2024dsbench}; users must obtain DSBench separately. Raw LLM responses are not redistributed; users must re-run experiments to obtain them. The benchmark can be extended with new tasks by implementing the \texttt{Task} interface.

\textbf{Maintenance plan.} The repository is maintained by the authors. Issues and pull requests are accepted via GitHub. The maintainers commit to:
\begin{itemize}[leftmargin=*,itemsep=1pt]
\item Responding to issues within 30 days.
\item Releasing compatibility patches for new LLM API versions.
\item Preserving backward compatibility of the manifest schema across minor versions.
\item Archiving major versions as tagged releases.
\end{itemize}

\textbf{Versioning.} The benchmark follows semantic versioning (\texttt{MAJOR.MINOR.PATCH}). The current release is v1.0.0. Breaking changes to the manifest schema or task definitions increment \texttt{MAJOR}; new tasks or metrics increment \texttt{MINOR}; bug fixes increment \texttt{PATCH}. Each release is tagged on GitHub with a corresponding Zenodo DOI for long-term archival.

\textbf{Intended use cases.} The benchmark is designed for: (1) evaluating LLM-agent failure modes on data-science tasks; (2) comparing diagnostic metrics (SFR, propagation depth, recovery rate) across models; (3) testing new verifier or repair strategies. It is \emph{not} intended for: (1) training LLMs (tasks have deterministic answers); (2) production deployment evaluation (the minimal ReAct harness differs from production systems); (3) cross-domain generalisation claims (the three suites cover data analysis, not all of data science).

\subsection{Propagation Depth Analysis}

\Cref{tab:propagation} reports the propagation depth distribution across all 3{,}940 failures. The average depth is 0.30 steps, meaning most failures are detected immediately. However, 262 failures (6.9\%) propagate to depth $\geq$ 2, indicating long-horizon failure spread where the agent continues building on a wrong intermediate result.

\begin{table}[t]
\centering
\caption{Propagation depth distribution (all 3{,}940 failures).}
\label{tab:propagation}
\small
\begin{tabular}{@{}ccc@{}}
\toprule
Depth & Failures & Percentage \\
\midrule
0 & 3{,}350 & 88.6\% \\
1 & 169 & 4.5\% \\
2 & 80 & 2.1\% \\
3 & 39 & 1.0\% \\
4 & 64 & 1.7\% \\
5 & 45 & 1.2\% \\
6 & 20 & 0.5\% \\
7 & 14 & 0.4\% \\
\midrule
$\geq$ 2 (long-horizon) & 262 & 6.9\% \\
\bottomrule
\end{tabular}
\end{table}
