\section{Discussion}
\label{sec:disc}

\subsection{Why Strong Models Fail Silently}
\label{sec:disc-why}

Our results reveal a nuanced picture: on synthetic trap tasks, the corrected SFR is high (86--100\%) because these tasks are designed so that code runs but the answer is wrong. On real UCI data, however, the SFR drops to 4\%, and on DSBench to 19\%. A null-model analysis ($R^2 = 0.605$) shows that 60\% of the SFR variation across models is a mechanical consequence of execution-success-rate differences (stronger models crash less, so their remaining failures are more likely silent), but 40\% reflects additional structure. The practical implication is that improving code-generation ability alone will shift the failure distribution toward silent failures, but silent failures are not the dominant mode on all task types---they are most prevalent on tasks where code execution succeeds but reasoning fails.

\subsection{Implications for Agent Deployment}
\label{sec:disc-impl}

The zero recovery rate (\Cref{sec:res-recovery}) has direct deployment consequences. An agent that never self-corrects silent failures will propagate wrong answers through multi-step pipelines, and the errors compound. Practitioners cannot rely on the agent to ``notice'' it is wrong; external verification is mandatory. However, our verifier ablation (\Cref{sec:res-verifier}) shows that simple rule-based verification is a double-edged sword: it helps weak models but harms strong ones. Effective verification likely requires model-specific calibration or learned verifiers, not hand-coded rules.

\subsection{The Bifurcation Phenomenon}
\label{sec:disc-bifurcation}

The failure bifurcation (\Cref{sec:res-bifurcation}) is partially mechanical ($R^2 = 0.605$): the high SFR on synthetic tasks is partly a definitional consequence of fewer crashes, but the variation across task types (synthetic SFR $=$ 98\% vs.\ UCI SFR $=$ 4\%) cannot be explained by execution success alone. We therefore characterise the bifurcation as a task-dependent phenomenon: tasks that allow code to run (synthetic traps) produce silent failures, while tasks that trigger code crashes (real data with complex formats) produce loud failures. This is not a universal ``phase transition'' but a task-type effect, and we report it as such rather than claiming a general law.

A detailed discussion of limitations and ethical considerations is provided in \Cref{sec:limits-ethics}.

\subsection{Negative Control: Oracle Repair Revisited}
\label{sec:disc-negative-control}

To test whether the oracle repair rate (\Cref{sec:causal}) genuinely reflects step-specific causal attribution, we ran a negative control on 56 failed tasks. The \emph{no-op} intervention runs the ground-truth code independently in a fresh sandbox, without any step replacement. If oracle repair truly measures step-level causality, the no-op rate should be substantially lower. As \Cref{tab:negative-control} shows, the two rates are identical (64.3\%), and the conservative true-positive rate (oracle succeeds \emph{and} no-op fails) is 0.0\%. This confirms that the oracle repair rate measures whether the ground-truth code produces the correct answer, \emph{not} whether replacing the originating step has a step-specific causal effect. We therefore report oracle repair as an upper bound on reparability rather than as evidence of root-cause localisation, and we acknowledge this as a limitation of the current counterfactual design.

\input{tables/table_negative_control}
