\section{Related Work}
\label{sec:related}

\subsection{Data-Science Agent Benchmarks}
The emergence of LLM-based data-science agents has motivated several benchmarks. DSBench~\citep{jing2024dsbench} collects 466 data-analysis and 74 data-modelling tasks from ModelOff and Kaggle, reporting that the best agent (GPT-4o) solves only 34\% of analysis tasks. DataSciBench~\citep{zhang2026datascibench} evaluates LLMs across the full data-science workflow with multi-dimensional metrics. DSAEval~\citep{sun2026dsaeval} covers real-world data-science problems spanning multiple stages. LongDS-Bench~\citep{xu2026longdsbench} specifically studies long-horizon agentic data analysis and shows that agents fail on iterative tasks. GRACE-DS~\citep{tsymbalov2026graceds} introduces a guarded reward-guided correction environment for AutoML agents. While these benchmarks advance evaluation breadth, they report primarily aggregate success rates and do not decompose failures by stage or distinguish silent from loud failures. \citet{moghadasi2026what} audit twelve agent-benchmark papers and find systematic under-reporting of evaluation details, motivating our fine-grained diagnostic metrics. Agent Laboratory~\citep{schmidgall2025agent} uses LLM agents as research assistants but does not diagnose failure modes. Our work is complementary: rather than proposing a new benchmark, we provide a diagnostic \emph{layer} that can be applied to any of these benchmarks to reveal where and why agents fail.

\subsection{LLM Agent Failure Analysis}
A recent wave of work studies how and why LLM agents fail. \citet{albayaydh2026beyond} synthesise tool-use, planning, and reasoning failures across benchmarks. ToolFailBench~\citep{soni2026toolfailbench} diagnoses tool-use failures by decomposing the tool-call pipeline. \citet{wu2026when} present a longitudinal taxonomy of silent failures in a production LLM agent runtime, and \citet{liu2026silent} frame silent failure as an entropy-driven inevitability of autonomous agents. \citet{mehta2026confident} identify ``confident and wrong'' semantic failures in coding agents, the closest conceptual precursor to our silent-failure notion, but study coding rather than data-science tasks and do not provide a stage-level taxonomy. TrajAudit~\citep{wang2026trajaudit} automates failure diagnosis for agentic coding systems via trajectory auditing. \citet{reddy2026reason} recover a silent policy-violation failure mode in tool-using agents via deterministic gates. \citet{zhang2026library} diagnose library drift as a silent failure in self-evolving skill libraries. Ekka~\citep{gu2026ekka} diagnoses silent errors in LLM \emph{inference} (serving), a different layer than agent-level silent failures. Our contribution relative to this body of work is a \emph{four-stage taxonomy} that localises silent failures within the agent loop and a \emph{counterfactual causal-replay} mechanism that attributes failures to specific steps.

\subsection{Causal Attribution and Failure Recovery}
\citet{shah2026causal} proposes Causal Agent Replay for counterfactual attribution of LLM-agent failures, which directly inspires our causal-replay module; we extend it to the data-science setting and integrate it with the four-stage taxonomy. On the recovery side, self-consistency~\citep{wang2022selfconsistency} samples multiple reasoning paths and votes, but targets reasoning errors rather than code-execution silent failures. Verification-based approaches~\citep{itkin2026delayed} use verifier or critic agents to suppress hallucinations, but \citet{itkin2026delayed} shows that delayed verification can destabilise multi-agent belief. Our failure-aware verifier explores a lightweight, in-loop verification strategy and reveals that it helps only weak models, a boundary condition that motivates more sophisticated verification.

\subsection{LLM-as-Judge and Evaluation Methodology}
Using LLMs to evaluate LLM outputs is now standard~\citep{li2025from,gao2025llmbased}, but LLM-as-judge introduces its own biases. \citet{mohammadi2025evaluation} survey evaluation and benchmarking of LLM agents. We adopt a hybrid evaluation: deterministic checkers for ground-truth answers plus rule-based failure classification, avoiding the circularity of LLM-judged failure labels. Our annotation protocol (100 traces, two annotators, Cohen's $\kappa$) follows inter-rater-reliability best practice from clinical and software-engineering empirical guidelines~\citep{baltes2025guidelines}.
