\section{Annotation Protocol and Results}
\label{app:annotation}

The final evaluation set contains 150 human-adjudicated failed traces: an earlier 47-trace tranche and 103 newly sampled traces. Three annotators independently label the new tranche while blinded to model and system predictions; each reproduces five duplicate QC traces exactly. Raw Fleiss' agreement is $\kappa=.350$ for stage (95\% CI [.235, .447]) and $.590$ for observability. Stage full agreement is 27.2\%; 87 traces undergo consensus adjudication. The final distribution is Output-Mismatch 77, Runtime 39, Answer-Error 22, Code-Generation 12, and Analytical-Plan 0. Raw labels, QC mappings, adjudications, and gold labels are released.

\section{Harness Ablation Details}
\label{app:harness}

\Cref{tab:harness-ablation} reports the full harness ablation results on synthetic tasks. We also ran the same three harnesses on all 23 UCI tasks (3 repetitions each), with consistent results: GPT-4o shows SFR of 100\% (H1), 31\% (H2), and 100\% (H3) on UCI, matching the synthetic pattern (100\%/30\%/100\%). This confirms silent failures are not an artifact of the minimal ReAct design across both task types.

\input{tables/table_harness_ablation}

\section{Recovery Benchmark Details}
\label{app:recovery}

The recovery benchmark (\Cref{sec:res-recovery-bench}) tests 100 failed traces (80 silent + 20 loud) under 6 feedback conditions, yielding 600 runs. Overall recovery rate is 15.7\%. The key finding is the asymmetry between failure types: loud failures recover at 36.7\% (44/120) while silent failures recover at only 10.4\% (50/480), confirming that silent failures remain substantially harder to correct even with explicit feedback signals.

\section{Reproducibility}
\label{app:repro}

All experiments use deterministic data generation (fixed seeds for synthetic tasks) and temperature-0 LLM calls. The framework includes a deterministic MockLLM that reproduces the full pipeline without API cost. Real-model experiments use the ChatAnywhere OpenAI-compatible endpoint. Total API cost: \$80. Code and data: \url{https://github.com/llmnjust-afk/KDD2027_Work2}.

\section{Data Availability}
\label{app:data-avail}

All code, data, and traces are available at \url{https://github.com/llmnjust-afk/KDD2027_Work2}. The release includes the 32-field manifest, the 150-trace human gold set with raw labels and adjudications, the 927-run relaxed-sandbox extension, deterministic baseline scripts, and dependency specifications. Synthetic tasks are self-contained; UCI data download at runtime, while DSBench requires its separately licensed source~\citep{jing2024dsbench}.
